A Survey on Ordered Binary Decision Diagrams

### 2015-09-14 paper.tex
Add new bound using universal hashing intro

\tbr

>>>>

Nevertheless, researches put some effort in improving this lower bound. In 2001,
Woelfel~\cite{WOELFEL01} published a new bound lower bound as well as a first 
nontrivial upper bound for the size of OBDDs representing $n$-bit integer
multiplication by utilizing the concept of \textit{universal hashing}. \tbr
